A molecular taxonomy of tumors independent of tissue-of-origin

### 2020-08-31 text/manuscript.Rmd
add Tim to acknowledgements

We wish to thank David Van Valen, Kate Lawrenson, Simon Knott, and Megan
Hitchens for critical reading of this manuscript, and Ivetth Corona for early
discussions and feedback.

>>>>

We wish to thank David Van Valen, Kate Lawrenson, Simon Knott, and Megan
Hitchens, for critical comments on this manuscript, and Tim Triche Jr for
suggested improvements to the preprint. We also thank Ivetth Corona for early
discussions and feedback.
